### 2017-10-01 TF-vldb2018/sec-expt.tex

%We next present an experimental study using both real-life and synthetic data.
We conducted four sets of experiments to evaluate the performance of
(1) \optgrouprec for the top-$k$ team formation problem,
(2) \inc for the dynamic top-$k$ team formation problem
\wrt single set of (a) pattern updates, (b) data updates, and (c) simultaneous pattern and data updates;
(3) \inc \wrt continuous sets of pattern and data updates; and
(4) the extra space cost of auxiliary structures used by \inc.

@@

%\subsection{Experimental Settings}
%We used the following real-life and synthetic datasets.
\vspace{-0.3ex}
\etitle{Data graphs.} We used two real-life and a synthetic dataset.

>>>>

%We next present an experimental study using both real-life and synthetic data.
We conducted four sets of experiments to evaluate the performance of
(1) \optgrouprec for the top-$k$ team formation problem,
(2) \inc for the dynamic top-$k$ team formation problem
\wrt single sets of (a) pattern updates, (b) data updates, and (c) simultaneous pattern and data updates,
(3) \inc \wrt continuous sets of pattern and data updates, and
(4) the extra space cost of auxiliary structures used by \inc.

@@

%\subsection{Experimental Settings}
%We used the following real-life and synthetic datasets.
\vspace{-0.3ex}
\etitle{Data graphs.} We used two real-life and a synthetic datasets.
